---
title: "FinalGroup8 Vignette"
author: "Group 8"
date: "2024-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first step to using this package is to install the package from github. To do this, we need to install the devtools package `install.packages(devtools)`. Then we use the following code to download the package from github.

```{r message=FALSE, warning=FALSE}
library(devtools)
install_github("AU-R-Programming/FinalProject_Group8")
library(FinalGroup8)
```

Now, the package is available for use.

We will demonstrate how to use this function with the `bank.csv` data, which can be found at https://archive.ics.uci.edu/dataset/222/bank+marketing. First, we need to install the data.

```{r message=FALSE, warning=FALSE}
setwd("~/Desktop/Auburn/Fall 2024/STAT 6210")
bank <- read.csv("bank.csv", sep = ";")
head(bank)
```

As you can see, the bank data contains 17 columns (16 predictors and 1 response variable). In order to use the `logistic_regression` function in the `FinalGroup8` package, we must prepare the data. First, we need to create a data frame that contains only the x (independent) variables.

```{r message=FALSE, warning=FALSE}
x <- bank[,1:16]
```

Then, we need to create a vector that contains the y (dependent) variable. We also *must* use the `as.factor` function to redefine the y-variable as a factor.

```{r message=FALSE, warning=FALSE}
y <- as.factor(bank[,17])
```

Now, the data has been prepared, and we can utilize the `logistic_regression` function. We run the function and store the results in a list `bank_model`.

```{r message=FALSE, warning=FALSE}
bank_model <- logistic_regression(x, y, B = 20, conf_level = 0.95)
```

Now, we can extract all the elements that were created by running the `logistic_regression` function. First, we can look at the estimated regression coefficients.

```{r message=FALSE, warning=FALSE}
bank_model$coefficient_estimates
```